---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Assessment Model:/nFits to Aggregated Fisheries Catch Data" 
    plot1stObs: TRUE
    numRecent: 30
    doc_type: "pdf"
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupModelFits.ACDs, include=FALSE}
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;
    plot1stObs<-params$plot1stObs;
    numRecent<-params$numRecent;
    
    ##set appendix letter
    app="A";
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=7.0, dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

#Model fits to aggregated fisheries catch data
Fits to the aggregated fisheries catch data available to the model(s) are presented in this section. Not all of the fits presented are necessarily included in the parameter optimization for each model; some fits to datasets for a particular model may be included for comparison purposes with other models which include those data in their optimization. The reader should consult the main assessment document to determine which fits are included in the optimization for any particular model.

\blandscape

#Fishery retained catch biomass

##Fits

```{r plotFits.FisheryRetainedCatchBiomass,results='asis',fig.height=5.5,fig.width=9.0,out.width="9.0in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.BiomassData(Models,
                                             fleet.type='fishery',
                                             catch.type='retained',
                                             plot1stObs=plot1stObs,
                                             verbose=FALSE,
                                             numRecent=numRecent);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo fits to fishery retained catch biomass data.\n\n")
    }
```
\FloatBarrier

\elandscape

##Z-scores

```{r plotFits.ZScores.FisheryRetainedCatchBiomass,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.ZScores.Biomass(Models,
                                                 fleet.type='fishery',
                                                 catch.type='retained',
                                                 verbose=FALSE);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo z-scores for fits to fishery retained catch biomass data.\n\n")
    }
```

\FloatBarrier

\blandscape

#Fishery retained catch abundance

##Fits

```{r plotFits.FisheryRetainedCatchAbundance,results='asis',fig.height=5.5,fig.width=9.0,out.width="9.0in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.AbundanceData(Models,
                                               fleet.type='fishery',
                                               catch.type='retained',
                                               plot1stObs=plot1stObs,
                                               verbose=FALSE,
                                               numRecent=numRecent);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo fits to fishery retained catch abundance data.\n\n")
    }
```

\FloatBarrier

\elandscape

##Z-scores

```{r plotFits.ZScores.FisheryRetainedCatchAbundances,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.ZScores.Abundance(Models,
                                                   fleet.type='fishery',
                                                   catch.type='retained',
                                                   verbose=FALSE);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo z-scores for fits to fishery retained catch abundance data.\n\n")
    }
```

\FloatBarrier

\blandscape

#Fishery total catch biomass

##Fits

```{r plotFits.FisheryTotalCatchBiomass,results='asis',fig.height=5.5,fig.width=9.0,out.width="9.0in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.BiomassData(Models,
                                             fleet.type='fishery',
                                             catch.type='total',
                                             plot1stObs=plot1stObs,
                                             verbose=FALSE,
                                             numRecent=numRecent);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo fits to fishery total catch biomass data.\n\n")
    }
```

\FloatBarrier

\elandscape

##Z-scores
```{r plotFits.ZScores.FisheryTotalCatchBiomass,results='asis',fig.height=8.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.ZScores.Biomass(Models,
                                                 fleet.type='fishery',
                                                 catch.type='total',
                                                 verbose=FALSE);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo z-scores for fits to fishery total catch biomass data.\n\n")
    }
```

\FloatBarrier

\blandscape

#Fishery total catch abundance

##Fits

```{r plotFits.FisheryTotalCatchAbundance,results='asis',fig.height=5.5,fig.width=9.0,out.width="9.0in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.AbundanceData(Models,
                                               fleet.type='fishery',
                                               catch.type='total',
                                               plot1stObs=plot1stObs,
                                               verbose=FALSE,
                                               numRecent=numRecent);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo z-scores for fits to fishery total catch abundance data.\n\n")
    }
```

\FloatBarrier

\elandscape

##Z-scores

```{r plotFits.ZScores.FisheryTotalCatchAbundance,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
    plts<-rCompTCMs::compareFits.ZScores.Abundance(Models,
                                                   fleet.type='fishery',
                                                   catch.type='total',
                                                   verbose=FALSE);
    if (!is.null(plts)){
        captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
        for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
        rm(plt,plts);
    } else {
        cat("\nNo z-scores for fits to fishery total catch abundance data.\n\n")
    }
```
