---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab  Model Parameters Comparison" 
    plot1stObs: TRUE
    doc_type: "pdf"
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        number_sections: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupParameterTables,echo=FALSE,results='hide'}
##input model list
Models<-params$Models;
plot1stObs<-params$plot1stObs;
doc_type<-params$doc_type;

##set knitr options for subsequent chunks
knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=3.5, dpi=300)

##set caption numbering
if (!exists("fig")){
  fig<-1;#figures
  tbl<-0;#tables
}

cases<-names(Models);
nCases<-length(cases);
```

\blandscape

\section{Parameters}

\subsection{Parameters at bounds}

The following tables list the parameters for each model case that ended up near the lower or upper limits set on the parameter in question. Here, the criterion for being "at" the bound is to be closer than 0.01% of the allowed range to either bound.

```{r printParametersAtBounds,results='asis'}
  mdfr<-rCompTCMs::extractMDFR.Results.ParametersAtBounds(Models);
  write.csv(mdfr,file="ModelParametersAtBounds.csv",row.names=FALSE);
  rCompTCMs::printResults.ParametersAtBounds(mdfr=mdfr,fontsize="tiny");
  rm(mdfr);
```

\clearpage

\subsection{Parameter estimates}

Estimated parameter values and associated standard deviations (from the ADMB std file) are presented in the following table for the model scenarios `r paste0(paste0(cases[1:(nCases-1)],collapse=", ")," and ",cases[nCases])`.

```{r printParamsTable, results="asis"}
  mdfr<-rCompTCMs::extractMDFR.Results.ParameterValues(Models);
  write.csv(mdfr,file="ModelParameterValues.csv",row.names=FALSE);
  rCompTCMs::printResults.ParameterValues(mdfr=mdfr,fontsize="tiny");
  rm(mdfr);
```

\elandscape
