---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: 'Tanner Crab Assessment Model:\nEstimated Survey Characteristics' 
    doc_type: "pdf"
    CharacteristicsForSurveys:
      !r list(plot1stObs=TRUE,
             fleets="all",
             selyears="all",
             avlyears="all",
             capyears="all",
             mxy=5,
             verbose=FALSE)
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupSurveyCharacteristics, include=FALSE}
  message("Starting modelComparisons.EstimatedCharacteristics.Surveys.Rmd")
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;
    plot1stObs<-params$CharacteristicsForSurveys$plot1stObs;
    message(paste0("verbose = ",params$CharacteristicsForSurveys$verbose,"\n"))
    
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=6.5, out.width="6.5in",dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

# Estimated survey characterisitics
A comparison of model-estimated survey characteristics such as catchability and size-specific selectivity functions, 
availability and size-specific availability functions, and size-specific capture probability functions is presented here.

\clearpage

## Survey catchability
"Catchability" here refers to the catchability of crab in a fully-selected size bin.

```{r ESCs.Catchability,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("Starting ESCs.Catchability")
  captions<-NULL;
  if (!is.null(params$CharacteristicsForSurveys$selyears)){
      plts<-rCompTCMs::compareResults.Surveys.Catchability(Models,
                                                           fleets=params$CharacteristicsForSurveys$fleets,
                                                           dodge=0,
                                                           showPlot=FALSE,
                                                           verbose=params$CharacteristicsForSurveys$verbose)
      captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
      for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
      rm(plt,plts);
  } else {
      cat(" Catchability plots are not provided for these model comparisons.\n\n");
  }
```

\FloatBarrier

\clearpage 

## Survey selectivity functions
Survey selectivity functions reflect size-specific catchability relative to a fully-selected size class.

```{r ESCs.Selectivity,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("Starting ESCs.Selectivity")
  captions<-NULL;
  if (!is.null(params$CharacteristicsForSurveys$selyears)){
      plts<-rCompTCMs::compareResults.Surveys.SelFcns(Models,
                                                      fleets=params$CharacteristicsForSurveys$fleets,
                                                      cast="y+x",
                                                      facet_grid="y~x",
                                                      mxy=params$CharacteristicsForSurveys$mxy,
                                                      years=params$CharacteristicsForSurveys$selyears,
                                                      dodge=0,
                                                      verbose=params$CharacteristicsForSurveys$verbose);
      captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
      for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
      rm(plt,plts);
  } else {
      cat(" Selectivity plots are not provided for these model comparisons.\n\n");
  }
```

\FloatBarrier

\clearpage 

## Survey availability
"Availability" here represents an overall multiplier on the size-specific availability functions described in the next section. 

```{r ESCs.Availability,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("Starting ESCs.Availability")
  captions<-NULL;
  if (!is.null(params$CharacteristicsForSurveys$avlyears)){
      plts<-rCompTCMs::compareResults.Surveys.Availability(Models,
                                                           fleets=params$CharacteristicsForSurveys$fleets,
                                                           years=params$CharacteristicsForSurveys$avlyears,
                                                           dodge=0,
                                                           showPlot=FALSE,
                                                           verbose=params$CharacteristicsForSurveys$verbose)
      captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
      for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
      rm(plt,plts);
  } else {
      cat(" Availability plots are not provided for these model comparisons.\n\n");
  }
```

\FloatBarrier

\clearpage 

## Survey availability functions
Survey availability functions reflect size-specific availability of crab to the survey gear over the entire survey area, 
possibly relative to the "most-available" size class (see the previous section for the availability multipliers when the 
size-specific availability functions are normalized to the most-available size class).

```{r ESCs.AvlFcns,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("Starting ESCs.AvlFcns")
  captions<-NULL;
  if (!is.null(params$CharacteristicsForSurveys$avlyears)){
      plts<-rCompTCMs::compareResults.Surveys.AvlFcns(Models,
                                                      fleets=params$CharacteristicsForSurveys$fleets,
                                                      cast="y+x",
                                                      facet_grid="y~x",
                                                      mxy=params$CharacteristicsForSurveys$mxy,
                                                      years=params$CharacteristicsForSurveys$avlyears,
                                                      dodge=0,
                                                      verbose=params$CharacteristicsForSurveys$verbose);
      captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
      for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
      rm(plt,plts);
  } else {
      cat(" Availability function plots are not provided for these model comparisons.\n\n");
  }
```

\FloatBarrier

\clearpage 

## Survey capture probability functions
Survey capture probability functions incorporate both catchability and size-specific selectivity, 
as well as availability and size-specific availability. These represent the proportion of survey-estimated 
crab abundance at size *z* after expansion to the survey area relative to the abundance of crab at size *z*
within the population.

```{r ESCs.CaptureProbs,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("Starting ESCs.CaptureProbs")
  captions<-NULL;
  if (!is.null(params$CharacteristicsForSurveys$capyears)){
      plts<-rCompTCMs::compareResults.Surveys.CaptureProbs(Models,
                                                           fleets=params$CharacteristicsForSurveys$fleets,
                                                           cast="y+x",
                                                           facet_grid="y~x",
                                                           mxy=params$CharacteristicsForSurveys$mxy,
                                                           years=params$CharacteristicsForSurveys$capyears,
                                                           dodge=0,
                                                           verbose=params$CharacteristicsForSurveys$verbose);
      captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
      for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
      rm(plt,plts);
  } else {
      cat(" Capture probability plots are not provided for these model comparisons.\n\n");
  }
```

