---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Assessment Model:\nEstimated Survey Quantities" 
    plot1stObs: TRUE
    doc_type: "pdf"
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 7.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupModelComparisons.EstimatedSurveyQuantities, include=FALSE}
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;
    plot1stObs<-params$plot1stObs;
    
    ##set appendix letter
    app="A";
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=3.5, dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

#Introduction
Model-estimated survey-related quantities such as time series of survey abundance, biomass, and size compositions are presented in this section. Note that these plots do not indicate model fit, because they only show estimated, not observed, quantitities.

#Estimated Survey abundance

```{r ESQs01.SurveyAbundance,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in"}
  plts<-rCompTCMs::compareResults.Surveys.Abundance(Models,
                                                    category='index',
                                                    cast="x",
                                                    facet_grid=x~.,
                                                    scales="free_y",
                                                    dodge=0,
                                                    showPlot=FALSE,
                                                    verbose=FALSE);
  res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  fig<-res$figno;
  rm(plts,res);
```

#Estimated survey biomass

```{r ESQs02.SurveyBiomass,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in"}
  plts<-rCompTCMs::compareResults.Surveys.Biomass(  Models,
                                                    category='index',
                                                    cast="x",
                                                    facet_grid=x~.,
                                                    scales="free_y",
                                                    dodge=0,
                                                    showPlot=FALSE,
                                                    verbose=FALSE)
  res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  fig<-res$figno;
  rm(plts,res);
```

#Estimated survey size compositions

```{r ESQs03.SurveySizeCompositions,results='asis',fig.height=8,fig.width=6.5}
  plts<-rCompTCMs::compareResults.Surveys.Abundance(Models,
                                                    category='index',
                                                    cast="x+z",
                                                    facet_wrap=~y,
                                                    showPlot=FALSE,
                                                    verbose=FALSE);
  res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  fig<-res$figno;
  rm(plts,res);
```


