---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Model Fits to Size Composition Data" 
    plot1stObs: TRUE
    doc_type: "pdf"
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupModelFits, include=FALSE}
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;
    plot1stObs<-params$plot1stObs;
    
    ##set appendix letter
    app="A";
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=7.0, dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

#Model fits to size composition data

##Mean survey size compositions

```{r plotFits.SurveyMeanSizeComps,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.MeanSizeComps(Models,fleet.type="survey",catch.type="index",plot1stObs=plot1stObs,showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier

##Fishery retained catch mean size compositions

```{r plotFits.MeanFisheryRetainedCatchSizeComps,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.MeanSizeComps(Models,fleet.type="fishery",catch.type="retained",plot1stObs=plot1stObs,showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier

\clearpage

##Fishery total catch mean size compositions

```{r plotFits.FisheryMeanTotalCatchSizeComps,results='asis',fig.height=7.0,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.MeanSizeComps(Models,fleet.type="fishery",catch.type="total",plot1stObs=plot1stObs,facet_grid='x~.',showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\begin{landscape}

\subsection{Survey size composition residuals}

```{r plotFits.SurveyZCsBubblePlotsIM,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  mdfr<-rCompTCMs::extractFits.ZScores.PrNatZ(Models,fleet.type="survey",catch.type="index",residuals.type='pearsons',verbose=FALSE);
  idx<-(mdfr$x=="male")&(mdfr$m=="immature");
  plts<-rCompTCMs::compareFits.ZScores.PrNatZ(mdfr=mdfr[idx,],fleet.type="survey",catch.type="index",residuals.type='pearsons',
                                              showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); fig<-fig+1;}
```

```{r plotFits.SurveyZCsBubblePlotsMM,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  mdfr<-rCompTCMs::extractFits.ZScores.PrNatZ(Models,fleet.type="survey",catch.type="index",residuals.type='pearsons',verbose=FALSE);
  idx<-(mdfr$x=="male")&(mdfr$m=="mature");
  plts<-rCompTCMs::compareFits.ZScores.PrNatZ(mdfr=mdfr[idx,],fleet.type="survey",catch.type="index",residuals.type='pearsons',
                                              showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); fig<-fig+1;}
```

```{r plotFits.SurveyZCsBubblePlotsIF,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  mdfr<-rCompTCMs::extractFits.ZScores.PrNatZ(Models,fleet.type="survey",catch.type="index",residuals.type='pearsons',verbose=FALSE);
  idx<-(mdfr$x=="female")&(mdfr$m=="immature");
  plts<-rCompTCMs::compareFits.ZScores.PrNatZ(mdfr=mdfr[idx,],fleet.type="survey",catch.type="index",residuals.type='pearsons',
                                              showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
for (plt in plts) {print(plt); fig<-fig+1;}
```

```{r plotFits.SurveyZCsBubblePlotsMF,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  mdfr<-rCompTCMs::extractFits.ZScores.PrNatZ(Models,fleet.type="survey",catch.type="index",residuals.type='pearsons',verbose=FALSE);
  idx<-(mdfr$x=="female")&(mdfr$m=="mature");
  plts<-rCompTCMs::compareFits.ZScores.PrNatZ(mdfr=mdfr[idx,],fleet.type="survey",catch.type="index",residuals.type='pearsons',
                                              showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); fig<-fig+1;}
```

\subsection{Effective Ns for survey size compositions}

```{r plotFits.SurveyEffectiveNs,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.EffectiveNs(Models,fleet.type="survey",category="index",showPlot=FALSE,verbose=FALSE)
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (i in 1:length(captions)) {captions[i]<-paste0("Input and effective sample sizes from retained catch size compositions from the ",captions[i],".");}
  for (plt in plts) {print(plt); fig<-fig+1;}
```

\subsection{Fishery retained catch size composition residuals}

```{r plotFits.FisheryRetainedCatchZCsBubblePlots,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.ZScores.PrNatZ(Models,fleet.type="fishery",catch.type="retained",residuals.type='pearsons',
                                             showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); fig<-fig+1;}
  rm(plt,plts);
```

\subsection{Effective Ns for retained catch size compositions}

```{r plotFits.RetainedCatchEffectiveNs,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.EffectiveNs(Models,fleet.type="fishery",category="retained",showPlot=FALSE,verbose=FALSE)
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (i in 1:length(captions)) {captions[i]<-paste0("Input and effective sample sizes from retained catch size compositions from the ",captions[i]," fishery.");}
  for (plt in plts) {print(plt); fig<-fig+1;}
```

\subsection{Fishery total catch size composition residuals}

```{r plotFits.FisheryTotalCatchZCsBubblePlots,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.ZScores.PrNatZ(Models,fleet.type="fishery",catch.type="total",residuals.type='pearsons',
                                              showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); fig<-fig+1;}
  rm(plt,plts);
```

\subsection{Effective Ns for total catch size compositions}

```{r plotFits.TotalCatchEffectiveNs,results='asis',fig.height=6.5,fig.width=9.0,out.width="9in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.EffectiveNs(Models,fleet.type="fishery",category="total",showPlot=FALSE,verbose=FALSE)
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (i in 1:length(captions)) {captions[i]<-paste0("Input and effective sample sizes from total catch size compositions from the ",captions[i]," fishery.");}
  for (plt in plts) {print(plt); fig<-fig+1;}
```

\end{landscape}
