---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Model Fits to Fishery Size Compositions" 
    fleets: "all"
    years: 'all'
    plot1stObs: TRUE
    nrow: 5
    ncol: 4
    useBars: TRUE
    usePins: FALSE
    usePinsAndPts: FALSE
    useLines: TRUE
    usePoints: TRUE
    lineSize: 1.0
    pointSize: 1.0
    alpha: 0.5
    stripText: 
        !r ggplot2::element_text()
    doc_type: "pdf"
    verbose: FALSE
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupModelFitsToSurveySizeComps, include=FALSE}
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;

    ##set appendix letter
    app="A";
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=3.5, dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

# Model fits to fishery size compositions, by year
Fits to the fishery size composition data available to the model(s) are presented in this section as line plots by year. Not all of the fits presented are necessarily included in the parameter optimization for each model; some fits to datasets for a particular model may be included for comparison purposes with other models which include those data in their optimization. The reader should consult the main assessment document to determine which fits are included in the optimization for any particular model.

# Retained catch size compositions

```{r plotFits.FisheryRetainedCatchZCsLinePlots,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.SizeComps(Models,
                                         fleet.type="fishery",
                                         catch.type="retained",
                                         fleets=params$fleets,
                                         years=params$years,
                                         plot1stObs=params$plot1stObs,
                                         nrow=params$nrow,
                                         ncol=params$ncol,
                                         useBars=params$useBars,
                                         usePins=params$usePins,
                                         usePinsAndPts=params$usePinsAndPts,
                                         useLines=params$useLines,
                                         usePoints=params$usePoints,
                                         lineSize=params$lineSize,
                                         pointSize=params$pointSize,
                                         alpha=params$alpha,
                                         stripText=params$stripText,
                                         showPlot=FALSE,
                                         verbose=params$verbose);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  #rm(plts,res);
```

\FloatBarrier

\clearpage

# Total catch size compositions

```{r plotFits.FisheryTotalCatchZCsLinePlots,results='asis',fig.height=6.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareFits.SizeComps(Models,
                                         fleet.type="fishery",
                                         catch.type="total",
                                         fleets=params$fleets,
                                         years=params$years,
                                         plot1stObs=params$plot1stObs,
                                         nrow=params$nrow,
                                         ncol=params$ncol,
                                         useBars=params$useBars,
                                         usePins=params$usePins,
                                         usePinsAndPts=params$usePinsAndPts,
                                         useLines=params$useLines,
                                         usePoints=params$usePoints,
                                         lineSize=params$lineSize,
                                         pointSize=params$pointSize,
                                         alpha=params$alpha,
                                         stripText=params$stripText,
                                         showPlot=FALSE,
                                         verbose=params$verbose);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```
