---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Model Fits to 'Other' Data" 
    doc_type: "pdf"
    ModelFitsToOtherData:
      !r list(plot1stObs=TRUE,
             minSizeForMaturityData=60,
             verbose=FALSE)
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupModelFits.OtherData, include=FALSE}
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;
    plot1stObs<-params$ModelFitsToOtherData$plot1stObs;
    verbose = params$ModelFitsToOtherData$verbose;
    
    ##set appendix letter
    app="A";
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=7.0, dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

# Model fits to "other" data

Fits to growth data and male maturity datasets by the model(s) are presented in this appendix. Not all of the fits presented are necessarily included in the parameter optimization for each model; some fits for a particular model may be included for comparison purposes with other models which include those data in their optimization. The reader should consult the main assessment document to determine which fits are included in the optimization for any particular model.

\clearpage

## Growth data

Fits to molt increment data from grow-out experiments are evaluated in this section.

```{r plotFits.GrowthData,echo=FALSE,results='asis',fig.height=7.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("plotting growth data \n\n")
  captions<-NULL;
  plts<-rCompTCMs::compareFits.GrowthData(Models,plot1stObs=plot1stObs,showPlot=FALSE,verbose=verbose)
  if (!is.null(plts)) {
    captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
    for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
    rm(plt,plts);
  } else{
    cat("No growth data was fit.\n\n")
  }
```

\FloatBarrier

\clearpage

## Maturity ogive data

In the male maturity dataset used in this assessment, a number of male crab less than 60 mm CW were classified as mature based on their chela height-to-carapace width ratios. For the purposes of fitting the data, these crab were assumed to be misclassified and to actually be immature. Consequently, data from size bins less than 60 mm CW, although possibly shown in the following plots comparing model predictions to observations, were not included in the likelihood used for model optimization and are not shown in the NLL and z-score plots.

```{r plotFits.MaturityData,echo=FALSE,results='asis',fig.height=7.5,fig.width=6.5,out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  message("plotting maturity ogives\n\n")
  captions<-NULL;
  message("params$minSizeForMaturityData = ",params$minSizeForMaturityData,"\n \n");
  plts<-rCompTCMs::compareFits.MaturityOgiveData(
                     Models,
                     minSize=params$ModelFitsToOtherData$minSizeForMaturityData,
                     plot1stObs=plot1stObs,
                     showPlot=FALSE,
                     verbose=verbose)
  if (!is.null(plts)) {
    captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
    for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
    rm(plt,plts);
  } else{
    cat("No maturity ogive data was fit.\n\n")
  }
```

