---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Model Population Quantities" 
    plot1stObs: TRUE
    doc_type: "pdf"
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupPopulationQuantities,include=FALSE}
  ##input model list
  Models<-params$Models;
  doc_type<-params$doc_type;
  
  ##set appendix letter
  app="A";
  ##set knitr options for subsequent chunks
  knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=6.5, out.width="6.5in",dpi=300)
  
  ##set caption numbering
  if (!exists("fig")){
    fig<-1;#figures
    tbl<-0;#tables
  }
  
  cases<-names(Models);
  nCases<-length(cases);
```

# Population quantities

Figures and tables in this section present comparisons between alternative model scenarios for estimated quantities (e.g., recruitment, abundance time series) describing the inferred Tanner crab population.

\blandscape

# Recruitment

```{r plotPopRecruitment,results='asis',fig.height=6.5,fig.width=8.5,out.width="8.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.Recruitment(Models,dodge=0,showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier

\elandscape

# Mature biomass

```{r plotPopMatureBiomass,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.MatureBiomass(Models,dodge=0,showPlot=FALSE,verbose=FALSE)
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier

\clearpage

# Population abundance

```{r plotPopAbundance,results='asis',fig.height=8.0,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.Abundance1(Models,dodge=0,type="N_yxm",facet_grid=x+m~.,scales="free_y",showPlot=FALSE,verbose=FALSE)
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier

\clearpage

# Population biomass

```{r plotPopBiomass,results='asis',fig.height=8.0,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.Biomass1(Models,dodge=0,type="B_yxm",facet_grid=x+m~.,scales="free_y",showPlot=FALSE,verbose=FALSE)
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier
