---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
params: 
    Models: none
    title: "Tanner Crab Model Population Processes" 
    plot1stObs: TRUE
    doc_type: "pdf"
output: 
    word_document: 
        reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        includes:
          in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
fontsize: 11pt
title: '`r params$title`'
---

```{r setupPopulationProcesses, include=FALSE}
    ##input model list
    Models<-params$Models;
    doc_type<-params$doc_type;
    
    ##set appendix letter
    app="A";
    ##set knitr options for subsequent chunks
    knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=6.5,out.width="6.5in", dpi=300)
    
    ##set caption numbering
    if (!exists("fig")){
      fig<-1;#figures
      tbl<-0;#tables
    }
    
    cases<-names(Models);
    nCases<-length(cases);
```

# Introduction

Figures and tables in this section present comparisons between alternative model scenarios for estimated rates (e.g., natural mortality) or other attributes (e.g., molt increments) describing inferred Tanner crab population processes.

# Natural mortality

```{r plotPopProcessNM,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.NaturalMortality(Models,dodge=0,showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\FloatBarrier

# Probability of terminal molt

```{r plotPopProcessPrM2M,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.PrM2M(Models,dodge=0,showPlot=FALSE,verbose=FALSE);
  captions<-paste("Probability of terminal molt.")
  print(plts);
  fig<-fig+1;
  #cap<-paste("\n  \nFigure &&figno. Probability of terminal molt.\n  \n")
  #plots<-list(); plots[[cap]]<-plts;
  #res<-wtsUtilities::printGGList(plots=plots,figno=fig,show=TRUE);
  #fig<-res$figno;
  #rm(plts,cap,plots,res);
```

\FloatBarrier

# Mean growth

```{r plotPopProcessMnGr,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.MeanGrowth(Models,dodge=0,showPlot=FALSE,verbose=FALSE);
  captions<-paste("Mean growth.")
  print(plts);
  fig<-fig+1;
  cap<-paste("\n  \nFigure &&figno. Mean growth.\n  \n")
  #plots<-list(); plots[[cap]]<-plts;
  #res<-wtsUtilities::printGGList(plots=plots,figno=fig,show=TRUE);
  #fig<-res$figno;
  #rm(plts,cap,plots,res);
```

\FloatBarrier

\clearpage

# Growth matrices
Growth matrices for each model case are compared as bubble plots in the following figure.

```{r plotPopProcessGMs1,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.GrowthMatrices(Models,showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\clearpage

The same growth matrices are compared in the following figure(s) as line plots for each pre-molt size bin, by sex.

```{r plotPopProcessGMs2,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.GrowthMatrices.LinePlots(Models,dodge=0,showPlot=FALSE,verbose=FALSE);
  captions<-wtsUtilities::getCaptionsFromGGPlotList(plts);
  #res<-wtsUtilities::printGGList(plots=plts,figno=fig,show=TRUE);
  #fig<-res$figno;
  for (plt in plts) {print(plt); cat("\n\n"); fig<-fig+1;}
  rm(plt,plts);
```

\clearpage

# Size distribution for recruits

```{r plotPopProcessRecZ,results='asis',fig.height=6.5,fig.width=6.5,fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  plts<-rCompTCMs::compareResults.Pop.RecSizeDistribution(Models,dodge=0,showPlot=FALSE,verbose=FALSE);
  captions<-paste("Size distribution for recruits.")
  print(plts);
  fig<-fig+1;
  #cap<-paste("\n  \nFigure &&figno. Size distribution for recruits.\n  \n")
  #plots<-list(); plots[[cap]]<-plts;
  #res<-wtsUtilities::printGGList(plots=plots,figno=fig,show=TRUE);
  #fig<-res$figno;
  #rm(plts,cap,plots,res);
```

\FloatBarrier
